---
title: "ass2"
output: html_document
---
# Third Algorithm - Tree Model
## Define the root directory
```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir ='~/Desktop/Ass2/Titanic')
getwd()
```

# Pre processing
## Read the train and the test data
```{r}
dftrain <- read.csv("train.csv")
dftest <- read.csv("test.csv")
```

## Plot the data(Survived\Not-Sex) to see if the Sex feature is important
```{r}
library(ggplot2)
qplot(Survived, data=dftrain, facets = ~Survived, fill=Sex, bins=1)

```

## Plot the data(Survived\Not-Embarked)  to see if the Embarkes feature is important
```{r}

qplot(Embarked, data=dftrain, facets = ~Survived, fill=Embarked)

```


## Save Survived column and then remove it from the train data in order to bind the ## train and the test data
```{r}
survivcopy=dftrain$Survived
dftrain<-subset(dftrain,select = -Survived)
```

## Save PassengerId data(need it two end model to check the results)
## Bind the train and the test data
## Define Pclass as a factor data
## Remove the cabin column-iirelevant
```{r}
pasidtrain<-dftrain$PassengerId
pasidtest<-dftest$PassengerId
df <- rbind(dftrain,dftest)[,-1]
df$Pclass <- as.factor(df$Pclass)
df<-subset(df,select= -Cabin)

summary(df)
```

## All the missing data of the Embarked column-'S'
```{r}
dftrain$Embarked[dftrain$Embarked==""] <-'S'

```

## Check at the Fare column which data is n.a
```{r}
 which(is.na(df$Fare))
```

## Complete the missing data at the Fare column-Median
```{r}
df$Fare[1044] <- median(df$Fare, na.rm=TRUE)
```

## Check the Age na data
```{r}
sum(is.na(df$Age))
```


## Using mice library to predict the missing age data
## Add title column
```{r}
library(mice)
set.seed(129)
mp<-mice(data = df[,!names(df) %in% c('PassengerId','Pclass','Name','Sex','Ticket')],method='rf')
mice_result <- complete(mp)
df$Age<-mice_result$Age

```
```{r}
df$Title <- gsub('(.*, )|(\\..*)', '', df$Name)
```


## Ordering the title column - the title helps to get better results
```{r}
head(df)
royal <- c('Dona', 'Lady', 'the Countess','Capt', 'Col', 'Don', 
                'Dr', 'Major', 'Rev', 'Sir', 'Jonkheer') 
df$Title[df$Title == 'Mlle']        <- 'Miss' 
df$Title[df$Title == 'Ms']          <- 'Miss'
df$Title[df$Title == 'Mme']         <- 'Mrs' 
df$Title[df$Title %in% royal]  <- 'royal'
```
```{r}
df$Family <- df$SibSp + df$Parch + 1
df$FsizeD[df$Family == 1] <- 'single'
df$FsizeD[df$Family < 5 & df$Family > 1] <- 'small'
df$FsizeD[df$Family > 4] <- 'big'
```


## Categorized the age data to 'Child'-under 18 and 'Adult'-over 18
## And factorized the data
```{r}
df$Child[df$Age < 18] <- 'Child'
df$Child[df$Age >= 18] <- 'Adult'
df$Child  <- factor(df$Child)

```

## Divide the data to train and test again after the pre proccessing
```{r}
sum(is.na(df$Age))
train1 <- df[1:891,]
test1 <- df[892:1309,]
```

## Create the tree model
```{r}
library(tree)
train1$Survived<- survivcopy
tree1 <- tree(Survived~ Pclass + Sex + Age + SibSp + Parch + 
                                            Fare + Embarked + Title + 
                                            FsizeD + Child, data = train1)
summary(tree1)
```

## Plot the tree
```{r}
plot(tree1)
text(tree1 ,pretty =0)
tree1
```

# Predict the test data using the tree model
```{r}
Pred1 <- predict(tree1, test1)
chkdf <- data.frame(PassengerId = dftest$PassengerId, Survived = Pred1,
                    gender = test1$Sex)
chkdf$final[chkdf$Survived <= 0.4]<- 0
chkdf$final[chkdf$Survived > 0.4]<- 1

```

## Check at the Fare column which data is n.a
```{r}
 which(is.na(df$Fare))
```

## Write the answers to the file
```{r}
submit <- data.frame(PassengerId = chkdf$PassengerId, Survived = chkdf$final)
write.csv(submit, file = "dtree.csv", row.names = FALSE)
```


